Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-02 paper/src/paper.tex
expe fix
advance paper

\documentclass[sigconf,review,anonymous]{acmart}
\setcopyright{rightsretained}

@@

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaicbandit-UniLu-Ga.pdf}

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaic-UniLu-Ga.pdf}

>>>>

\documentclass[sigconf,anonymous]{acmart}
\setcopyright{rightsretained}

@@

Table~\ref{tab:strat} reports the average total waiting time performance
improvement over EASY(FCFS,40h) of all the proposed strategies along with the
random variant.

We make the following observations.

\paragraph
\textbf{FCFS vs Random.} Note that randomly taking a policy in the search
set defined in ~\ref{subsec:policies} gives already a much better performance
than EASY(FCFS). This is due

\paragraph
\textbf{Simulated Feedback finds the best policy}
\paragraph
\textbf{Noisy simulations are useful.}
\paragraph
\textbf{Full vs Bandit feedback}

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaicbandit-ANL-Intr.pdf}

@@

\begin{figure}[]
  \centering
  \includegraphics[scale=0.6]{figures/mosaic-ANL-Intr.pdf}
